### 2015-03-03 ResearchNotes/Notes.Rmd
Page 16

This is an R Markdown document. Markdown is a simple formatting syntax for authoring web pages (click the **Help** toolbar button for more details on using R Markdown).

When you click the **Knit HTML** button a web page will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(cars)
```

>>>>

Load in the raw data.
```{r}
RECS <- read.csv("~/Research/EnergyEthnicity/Data/recs2009_public.csv")

summary(RECS)

```
